### 2023-02-23 main.tex
Re-named chapter 3
Modified notebook environments and added new material as inputs
Change list:
Added % to environments to prevent interpretation as returns
Made code listing boxes breakable
Made outlines white because they appeared on broken boxes regardless of other settings
Adjusted indent

% PACKAGE AND ENVIRONMENT CONFIGURATIONS
\usepackage{amsmath}
\usepackage{graphicx}

% Code listings
\usepackage[outputdir=out]{minted}
\usepackage{tcolorbox}
\usepackage{lmodern}

@@

\newlength{\promptwidth}
\setlength{\promptwidth}{0.5in}

@@

\newenvironment
{NotebookIn}
{
 \VerbatimEnvironment
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   size=fbox,
                   colback=bgcolor,
                   left skip=\promptwidth,
                   title=\prompt{In}{incolor},
                   attach title to upper]
 \begin{minted}{python}
}
{
 \end{minted}
 \end{tcolorbox}
}

\newenvironment
{NotebookOut}
{
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   size=fbox,
                   colback=white,
                   left skip=\promptwidth,
                   title=\prompt{Out}{outcolor},
                   attach title to upper]
 \\ \ttfamily
}
{
 \end{tcolorbox}
}

\newenvironment
{NotebookImage}
{
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   size=fbox,
                   colback=white,
                   left skip=\promptwidth,
                   title=\prompt{Out}{outcolor},
                   attach title to upper]
 \\
}
{
 \end{tcolorbox}
}

@@

\chapter{Software tools and tutorials}
\graphicspath{{chapter3/}}
\input{chapter3/chapter3.tex}

@@

\chapter{Supporting information for chapter 1}
\graphicspath{{chapter1/figures/}}
\input{chapter1/chapter1_supporting.tex}

>>>>

% PACKAGE AND ENVIRONMENT CONFIGURATIONS
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\!\max}
\DeclareMathOperator*{\argmin}{arg\!\min}

\usepackage{graphicx}

% Code listings
\usepackage[outputdir=out]{minted}
\usepackage{tcolorbox}
\tcbuselibrary{breakable}
\tcbset{colframe=white}
\usepackage{lmodern}

@@

\newlength{\promptwidth}
\setlength{\promptwidth}{0.375in}

@@

\newenvironment
{NotebookIn}
{%
 \VerbatimEnvironment%
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   breakable,
                   size=fbox,
                   colback=bgcolor,
                   left skip=\promptwidth,
                   title=\prompt{In}{incolor},
                   attach title to upper]%
 \begin{minted}{python}%
}
{%
 \end{minted}%
 \end{tcolorbox}%
}

\newenvironment
{NotebookOut}
{%
 \VerbatimEnvironment%
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   breakable,
                   size=fbox,
                   colback=white,
                   left skip=\promptwidth,
                   title=\prompt{Out}{outcolor},
                   attach title to upper]%
 \begin{minted}{text}%
}
{%
 \end{minted}%
 \end{tcolorbox}%
}

\newenvironment
{NotebookImage}
{%
 \begin{tcolorbox}[sharp corners,
                   frame empty,
                   size=fbox,
                   colback=white,
                   left skip=\promptwidth,
                   title=\prompt{Out}{outcolor},
                   attach title to upper]%
 \\%
}
{%
 \end{tcolorbox}%
}

@@

\chapter{Tools and tutorials for fitting mixture models and HMMs}
\graphicspath{{chapter3/}}
\input{chapter3/introduction.tex}
\input{chapter3/training_tutorial}

@@

\chapter{Supporting information for chapter 1}
\label{appendix:a}
\graphicspath{{chapter1/figures/}}
\input{chapter1/chapter1_supporting.tex}

\chapter{Supporting information for chapter 3}
\label{appendix:b}
\setlength{\promptwidth}{0in}  % No indent for appendix code
\input{chapter3/training_tutorial_supporting.tex}
